%% ============================================================
%%  RAJ PORWAL — Curriculum Vitae
%%  Compiler : pdfLaTeX  (works on Overleaf default settings)
%% ============================================================

\documentclass[10pt, a4paper]{article}

% ── Encoding & fonts ──────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

% ── Layout ────────────────────────────────────────────────
\usepackage[
  top=16mm, bottom=16mm,
  left=18mm, right=18mm
]{geometry}

% ── Packages ──────────────────────────────────────────────
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{soul}          % letter spacing via \textls
\usepackage{relsize}       % relative font sizes

% ── Colours ───────────────────────────────────────────────
\definecolor{ink}{HTML}{1a1612}
\definecolor{mid}{HTML}{5a4f45}
\definecolor{faint}{HTML}{9a8e82}
\definecolor{accent}{HTML}{c84b0f}
\definecolor{accentB}{HTML}{2a5caa}
\definecolor{tagbg}{HTML}{ede8e0}
\definecolor{rule}{HTML}{cec6bc}

% ── Hyperlinks ────────────────────────────────────────────
\hypersetup{
  colorlinks = true,
  urlcolor   = accentB,
  linkcolor  = accentB,
  pdftitle   = {Raj Porwal - CV},
  pdfauthor  = {Raj Porwal}
}

% ── Base colour ───────────────────────────────────────────
\color{ink}

% ── Spacing ───────────────────────────────────────────────
\setlength{\parskip}{3.5pt}
\setlength{\parindent}{0pt}

% ── Section style ─────────────────────────────────────────
\titleformat{\section}
  {\small\scshape\color{faint}\ls{150}}
  {}{0em}{}
  [\vspace{1pt}{\color{rule}\hrule height 0.4pt}\vspace{3pt}]

\titlespacing{\section}{0pt}{18pt}{7pt}

% ── Subsection (project names) ────────────────────────────
\titleformat{\subsection}
  {\normalsize\itshape\color{ink}}
  {}{0em}{}

\titlespacing{\subsection}{0pt}{12pt}{1pt}

% ── letter-spacing helper ─────────────────────────────────
\sodef\ls{}{.18em}{.4em}{.4em}

% ── Custom commands ───────────────────────────────────────

% \cvtag{text} — grey pill tag
\newcommand{\cvtag}[1]{%
  \colorbox{tagbg}{%
    \texttt{\relsize{-2}\color{mid}\,#1\,}%
  }\hspace{1.5pt}%
}

% \edentry{Institution}{Degree/Detail}{Status}
\newcommand{\edentry}[3]{%
  \vspace{3pt}%
  \textbf{#1}\hfill{\texttt{\relsize{-2}\color{faint}#3}}\\[-1pt]
  {\small\color{mid}#2}%
  \vspace{3pt}%
}

% \projhead{Title}{Tagline}
\newcommand{\projhead}[2]{%
  \subsection*{#1}%
  \vspace{-3pt}%
  {\texttt{\relsize{-2}\color{faint}#2}}%
  \vspace{3pt}%
}

% thin rule between projects
\newcommand{\pdiv}{%
  \vspace{4pt}%
  {\color{rule}\hrule height 0.3pt}%
  \vspace{8pt}%
}

% ── No page numbers ───────────────────────────────────────
\pagestyle{empty}

%% ============================================================
\begin{document}
%% ============================================================

% ── HEADER ───────────────────────────────────────────────
{\LARGE\textbf{Raj Porwal}}

\vspace{5pt}

{\small\color{mid}%
  \href{mailto:raazporwal6@gmail.com}{raazporwal6@gmail.com}%
  \enspace\textbullet\enspace 7078525809%
  \enspace\textbullet\enspace Ghaziabad, Uttar Pradesh%
}

{\small\color{mid}%
  \href{https://linkedin.com/in/raj-porwal-329493216}{linkedin.com/in/raj-porwal-329493216}%
  \enspace\textbullet\enspace%
  \href{https://twitter.com/raaz_porwal}{@raaz\_porwal}%
}

\vspace{5pt}
{\color{rule}\hrule height 0.8pt}
\vspace{10pt}

% ── ABOUT ────────────────────────────────────────────────
\section{\ls{about}}

CS undergrad building software that thinks and acts on its own. My work sits at the intersection of AI agents, backend systems, and real-world problems --- things that run unsupervised or talk to hardware. Competed in 10+ hackathons because there's nothing quite like shipping something real in 36 hours and watching it work.

% ── EDUCATION ────────────────────────────────────────────
\section{\ls{education}}

\edentry{ABES Engineering College, Ghaziabad}{B.Tech --- Computer Science \& Engineering}{Pursuing}
\edentry{Jyotri Academy, Bharthana, Etawah}{12\textsuperscript{th} Standard}{Completed}
\edentry{Jyotri Academy, Bharthana, Etawah}{10\textsuperscript{th} Standard}{Completed}

% ── SKILLS ───────────────────────────────────────────────
\section{\ls{skills}}

\begin{tabularx}{\linewidth}{@{} >{\color{faint}\texttt{\relsize{-2}}}l X @{}}
  AI / Agents  & \cvtag{Agentic AI} \cvtag{LLM Integration} \cvtag{RAG Systems} \cvtag{Multi-step Reasoning} \\[5pt]
  Vision       & \cvtag{YOLO} \cvtag{OpenCV} \cvtag{Computer Vision} \\[5pt]
  Backend      & \cvtag{Python} \cvtag{Java} \cvtag{REST APIs} \cvtag{System Design} \\[5pt]
  Full Stack   & \cvtag{Frontend} \cvtag{Backend} \cvtag{Web Dev} \\[5pt]
  DevOps       & \cvtag{CI/CD} \cvtag{GitHub Actions} \cvtag{Docker} \\[5pt]
  Hardware     & \cvtag{ESP32} \cvtag{IoT} \cvtag{Embedded Systems} \\[5pt]
  Other        & \cvtag{Razorpay API} \cvtag{Time Series} \cvtag{ML} \cvtag{Data Viz} \\
\end{tabularx}

% ── PROJECTS ─────────────────────────────────────────────
\section{\ls{projects}}

\projhead{Chakravyuh AI}{the scammer's worst nightmare}

Most anti-scam tools flag and block. Chakravyuh AI goes further --- an autonomous agent that \textbf{actively engages with scammers} in real conversation, wastes their time, learns their tactics, and protects real people. Built with multi-turn LLM reasoning and an adaptive response strategy.

\smallskip
\cvtag{Agentic AI} \cvtag{LLM} \cvtag{Python} \cvtag{Multi-turn Reasoning} \cvtag{NLP}

\pdiv

\projhead{NAV Predictor}{mutual fund intelligence for everyday investors}

Predicts the next NAV (Net Asset Value) of mutual funds using time-series models and delivers a plain \textbf{Buy / Hold / Sell} recommendation. Interactive graphs show historical NAV alongside the predicted curve --- users see the reasoning, not just the answer.

\smallskip
\cvtag{Python} \cvtag{Time Series} \cvtag{ML} \cvtag{Data Viz} \cvtag{Finance}

\pdiv

\projhead{CI/CD Pipeline Healer}{DevOps that fixes itself}

When a pipeline breaks, this agent diagnoses the failure, writes the fix, and opens a \textbf{GitHub Pull Request} automatically. No manual debugging, no Slack pings.
Live: \href{https://ai-dev-autonomous-ci-cd-healing-age.vercel.app/}{\texttt{ai-dev-autonomous-ci-cd-healing-age.vercel.app}}

\smallskip
\cvtag{Python} \cvtag{GitHub Actions} \cvtag{Agentic AI} \cvtag{DevOps}

\pdiv

\projhead{CampusAI}{RAG for campus life}

A retrieval-augmented AI assistant that answers questions using actual institutional documents --- circulars, timetables, exam schedules. Grounded answers with source citations, not hallucinations.

\smallskip
\cvtag{RAG} \cvtag{LLM} \cvtag{Vector DB} \cvtag{Python}

\pdiv

\projhead{Coaching Website}{full-stack institute management}

Notes upload, marks entry, student dashboards, teacher controls, role-based access. Built for and used by actual students at a coaching institute.

\smallskip
\cvtag{Full Stack} \cvtag{Web Dev}

\pdiv

\projhead{YOLO Object Detection}{real-time vision}

Object detection pipeline using YOLOv8. Runs on live camera feeds. Built end-to-end from frame capture to bounding box output.

\smallskip
\cvtag{Python} \cvtag{YOLO} \cvtag{OpenCV} \cvtag{Deep Learning}

\pdiv

\projhead{Home Automation with LLM + ESP32}{your house, but it listens}

Connected an LLM to an ESP32 microcontroller. Say what you want --- the model parses intent and sends the right command to hardware over serial/MQTT.

\smallskip
\cvtag{ESP32} \cvtag{LLM} \cvtag{IoT} \cvtag{Python} \cvtag{Embedded}

\pdiv

\projhead{Diwali Donation Website}{simple giving, done right}

Clean donation platform with Razorpay integration. Mobile-friendly, handled real payments, shipped fast.

\smallskip
\cvtag{Web Dev} \cvtag{Razorpay} \cvtag{JavaScript}

% ── ACHIEVEMENTS ─────────────────────────────────────────
\section{\ls{achievements}}

\begin{itemize}[leftmargin=1.4em, itemsep=2pt, topsep=2pt]
  \item Participated in \textbf{10+ national-level hackathons} across India
  \item Reached \textbf{semifinals} at RIFT Noida 24-hour Hackathon (CI/CD Pipeline Healer)
  \item Building production-level agentic AI systems as an undergraduate
\end{itemize}

% ── CONTACT ──────────────────────────────────────────────
\section{\ls{contact}}

\begin{tabularx}{\linewidth}{@{} >{\color{faint}\texttt{\relsize{-2}}}l X @{}}
  Email    & \href{mailto:raazporwal6@gmail.com}{raazporwal6@gmail.com} \\[4pt]
  Phone    & 7078525809 \\[4pt]
  LinkedIn & \href{https://linkedin.com/in/raj-porwal-329493216}{linkedin.com/in/raj-porwal-329493216} \\[4pt]
  Twitter  & \href{https://twitter.com/raaz_porwal}{@raaz\_porwal} \\[4pt]
  Location & Ghaziabad, Uttar Pradesh \\
\end{tabularx}

\end{document}
%% ============================================================
